% about
\def\MyName{Prakhar Gupta}
\def\MyDegreeType{Undergraduate}
\def\MyBranch{Computer Science and Engineering}
\def\MyYear{Fourth}
\def\MyAddress{62-A, Kurmitola, Azamgarh}
\def\MyEmail{prakhar.gupta.21031@iitgoa.ac.in}
\def\MyPhone{+91 8858968971}

%% --- links ---
\newcommand{\MyLinks}{
	LinkedIn: \Link{https://in.linkedin.com/in/prakhar-gupta-b5331124b}{Prakhar Gupta}
}

\newcommand{\github}{
	Github: \Link{https://github.com/prakhar619}{prakhar619}
}

%% --- education ---
\newcommand{\EducationData}{%%
	\MyDegree     {BTech, Computer Science and Engineering}
	\MyInstitute  {Indian Institute of Technology Goa}
	\MyScore      {CGPA : \textbf{7.49/10}}
	\MyEduComment {\hspace*{15mm}}
	\MyEduDate    {2021 -- Present}
	%
    \hline
	\MyDegree     {Class 12, CBSE}
	\MyInstitute  {St.Xavier's High School, Ailwal}
	\MyScore      {Aggregate: \textbf{93.2} \%}
	\MyEduComment { \hspace*{15mm}}
	\MyEduDate    {2019  --  2021}
  
	%
    \hline
	\MyDegree     {Class 10, ICSE}
	\MyInstitute  {Jyoti Niketan School, Atlas Tank}
	\MyScore      {Aggregate: \textbf{95.4} \%}
	\MyEduComment { \hspace*{15mm}}
	\MyEduDate    {2017  --  2019}
   %
    \hline
}
%% --- projects ---
\newcommand{\ProjectData}{
	%%
	\ListItem
	{Simple Physics Engine \Link{https://github.com/prakhar619/Simple-Physics-Engine}{[Github]}}
	{( Mar 24  --  Present)}
	{
	\item Designed Physics Engine for point objects, rigid bodies to simulate their interaction in different environments based on principles of classical mechanics.
	\item Used \textbf{ C++ with SDL2(Simple DirectMedia Layer)} library based on OpenGL provided efficient low-level way to handle graphics, audio, input and other multimedia functionalities.
        \item Extended  application simulator to \textbf{Multi Thread} for efficient handling of user input and Physics using Thread STL, synchronizing between different threads using mutex yielding 30\% faster computation time.
	\item Created key component features like entity, \textbf{motion dynamics}, \textbf{collision detection and handling}, fixed and variable time stepping, FPS management from ground up.
	}
        %%
	\ListItem
	{Open Maps Navigator\Link{https://github.com/prakhar619/openMap/}{[Github]}}
	{(Aug 23  --  Nov 23)}
	{
	\item Coded \textbf{OpenStreetMap} Navigation, an open source Google Map alternative, using OSM raw data, leveraging the extensive and constantly updated OSM database.
	\item  Constructed \textbf{POI (Point of Interest)} special feature to discover more than 100 nearby points of interest such as restaurants, cafes, parks, and landmarks within user's vicinity.
	\item Executed heuristic based algorithms like \textbf{A* Search} providing 67\% faster result than DFS and BFS to navigate in real world with turn-by-turn directions, estimated travel times, and distance information to reach their destinations efficiently.
	}
	%%
	\ListItem
	{Lab Coordinator \Link{https://github.com/prakhar619/Lab-Management}{[Github]}}
	{(Feb 24  --  Mar 24)}
	{
	\item Deployed Lab assessment web application for seamless coordinating between students, TAs and other faculties managing multiple hierarchical user login and respective privileges, tested for more than 50 simultaneous logins.
	\item Used \textbf{SQL} based relation database management system SQLite, an open source which supports ACID (Atomicity, Consistency, Isolation, Durability) transactions providing query execution time of less than 1 millisecond.
	\item Developed using \textbf{NodeJS} and \textbf{EJS} for accessing Javascript runtime environment and Javascript template engine respectively.
        \item Constructed the Backend of \textbf{User Management System}, \textbf{Viva Scheduling}, Grading Management, Analytics and Reporting for efficient coordination and ensuring seamless experience for both students and examiners.
	}

	%%
        \ListItem
	{AI Pacman Project\Link{https://github.com/prakhar619/cs188_Project}{[Github]}}
	{(Sept 23  --  Nov 23)}
	{
	\item Implemented \textbf{10+ AI algorithms} as part of academic lab in python.
	\item Performed AI searching like \textbf{Uninformed} and \textbf{Informed search} methods,\textbf{ CSPs} (constraint satisfaction problems consisting of backtracking search, forward checking as well as constraint propagation. 
        \item Integrated Game Playing technique comprising of \textbf{ Minimax Search} and their optimisation like\textbf{ alpha-beta pruning} and evaluation heuristic approximation improving speed by 32\% for bigger trees.
	}
}
% --- skills ---
\newcommand{\SkillsTable}{
	\SkillsRow
	{Programming Skills:}
	{C, C++, C\#, Python, Java, Haskell, JavaScript, Bash, R, Prolog, VHDL, SQL, Mongoose, MIPS Assembly, CUDA.}
	\SkillsRow
	{Software Skills:}
	{Auto-CAD, Solid works, LaTex, Git, GitHub, VS, VS Code, Vivado Xilinx, IntelliJ IDEA, Anaconda.}
        \SkillsRow
        {Frameworks/Libraries and OS:}
        {Ubuntu, Fedora, Windows,  Node,  Express, Spring Boot, Bootstrap, React, MongoDB, MySql, TensorFlow, Sci-kit-learn, SDL, Unity, Posix.}
	\SkillsRow
	{Relevant Coursework}
	{Data Structures and Algorithms, Algorithm Design, Computer Networks, Machine Learning, Artificial Intelligence, Probability and Statistics, Optimisation, Computer Architecture, Compiler Design, Unix Tools. }

}

%% --- positions of responsibility ---
\newcommand{\PorTable}{%%
  	\PorItem
		{Wing Representative}
		{Hostel Wing Representative in Student Panchayat}
		{(2022 -- 2023)}
	\PorItem
		{Core-Member}
		{Alpha - Finance Club of IIT Goa }
		{(Mar 23)}
	\PorItem
		{Event Overseer}
		{Cepheus KBC Event Overseer}
		{(2023 -- 2024)}
}
%% --- achievements ---
 %% \newcommand{\AchievementsData}{%%
%%	\StarItem {} {(2023)}
%% }
%% --- hobbies ---
\newcommand{\HobbiesData}{%%
	\StarItem {Committed to environmental stewardship, volunteering with Varaha, the Climate Change Society of IIT Goa, to clean various beaches.} {}
        \StarItem{Gaming enthusiast, engaging in fps, strategic, indie and open-world gameplays.} {}
        \StarItem{Competitive table tennis player, participating in tournaments and friendly matches in spare time.} {}
        \StarItem{Dedicated bookworm with a love for literature, exploring diverse genres and authors.} {}
}

% sizes
\def\FontSize{9pt}
\def\HMargin{12mm}
\def\TMargin{10mm}
\def\BMargin{10mm}
\def\LineSpacing{1.0}
\def\ItemSpacing{0.2em}


\input{./template}